---
title: "SimpLin-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SimpLin-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction
This Vignette gives an overview of the `SimpLin` package. This primary functionality
of this package is to fit a simple linear regression model to an input of two
numeric vectors.

# Install
To install this package proceed with the following.
```{r setup}
# install.packages("devtools") # if not installed
# devtools::install_github("dharmahoy/STAT600-HW1-SimpLinHoy")
library(SimpLin)
```

# Typical Usecase
When provided with the correct input type, the package will operate as follows.
```{r}
exampleX <- c(1,5,7,9,11,12,15)
exampleY <- c(2,7,9,10,15,20,3)
SimpLinR(exampleX, exampleY)
```

# Catching Errors
If vectors of different lengths are provided an error message will be shown
and execution will be stopped.
```{r}
exampleX <- c(1,5,7,9,11)
exampleY <- c(2,7,9,10,15,20,3)
# SimpLinR(exampleX, exampleY) # run this example to see error message
```

If the vectors are not numeric an error message will be shown and execution 
will be stopped.
```{r}
exampleX <- "foo"
exampleY <- "bar"
# SimpLinR(exampleX, exampleY) # run this example to see error message
```
