---
title: "SimpLin_Hoy"
author: "Dharma Hoy"
date: "2025-09-04"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to myRcppPackage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
This Vignette gives an overview of the `SimpLin` package. This primary functionality
of this package is to fit a simple linear regression model to an input of two
numeric vectors.

# Install
To install this package proceed with the following.
```{r}
# install.packages("devtools") # if not installed
# devtools::install_github("dharmahoy/STAT600-HW1-SimpLinHoy")
```

# Typical Usecase
When provided with the correct input type, the package will operate as follows.
```{r}
exampleX <- c(1,5,7,9,11,12,15)
exampleY <- c(2,7,9,10,15,20,3)
fitModel(exampleX, exampleY)
```

# Catching Errors
If vectors of different lengths are provided the following error message 
will be shown.
```{r}
exampleX <- c(1,5,7,9,11)
exampleY <- c(2,7,9,10,15,20,3)
fitModel(exampleX, exampleY)
```

If the vectors are not numeric the following error message will be shown.
```{r}
exampleX <- "foo"
exampleY <- "bar"
fitModel(exampleX, exampleY)
```

